\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[scale=0.85,top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage{hyperref}

\begin{document}
\pagestyle{empty}

\begin{flushleft}
\textbf{Omar Haggag}\\
Cairo, Egypt\\
+20 111 664 1976\\
\href{mailto:omarhaggag72@example.com}{omarhaggag72@example.com}\\
\href{https://linkedin.com/in/omarhaggagpy}{linkedin.com/in/omarhaggagpy}\\
\href{https://github.com/OmarHaggag}{github.com/OmarHaggag}
\end{flushleft}

\vspace{1em}
\begin{flushright}
\today
\end{flushright}

\vspace{1em}
\begin{flushleft}
Hiring Manager\\
Principal Engineer Design Enablement PDK -- Device Library Developer\\
Silicon Photonics Team\\
{[}Company Name{]}\\
{[}Company Address{]}
\end{flushleft}

\vspace{1em}
Dear Hiring Manager,

I am writing to express my strong interest in the Principal Engineer Design Enablement PDK position for Silicon Photonics. With over 5 years of experience as an EDA \& Infrastructure Engineer at Si-Vision, I have developed deep expertise in PDK development, device library creation, and CAD automation that I believe would be valuable to your silicon photonics team.

In my current role, I have led PDK development and fixes across multiple nodes (40nm, 22nm, 12nm), implementing PCell corrections and TCL callback scripts. I have developed custom SKILL automation for Cadence Virtuoso, including utilities to import DSPF-like netlist files and automatically generate schematic symbols suitable for simulation. My experience spans both commercial EDA tools (Custom Compiler, ICV, StarRC, PrimeSim) and open-source alternatives (Xschem, Magic, OpenLane).

I want to be transparent with you: I do not have prior hands-on experience with Silicon Photonics specifically. However, I am genuinely fascinated by the field and deeply interested in learning everything about it -- from waveguide fundamentals to photonic device physics and PDK implementation. My background in device library development, parameterized cells, and EDA tool automation provides a solid foundation, and I am committed to rapidly acquiring the specialized knowledge required for photonic IC design.

My experience debugging complex PCell issues, developing callback scripts, and automating layout workflows has prepared me to tackle the unique challenges of photonic device modeling. I am particularly drawn to this opportunity because it would allow me to apply my CAD expertise while expanding into an exciting, cutting-edge domain.

I would welcome the opportunity to discuss how my skills in PDK development, device library automation, and EDA infrastructure could contribute to your silicon photonics initiatives, and how I can quickly come up to speed on the photonics-specific aspects of the role. Thank you for considering my application.
\vspace{2em}
Sincerely,

\vspace{2em}
Omar Haggag

\end{document}

