\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[scale=0.85]{geometry}
\usepackage{hyperref}

% Personal Information
\signature{Omar Haggag}
\address{
    Omar Haggag\\\\
    Cairo, Egypt\\\\
    +20 111 664 1976\\\\
    \href{mailto:omarhaggag72@example.com}{omarhaggag72@example.com}\\\\
    \href{https://linkedin.com/in/omarhaggagpy}{linkedin.com/in/omarhaggagpy}\\\\
    \href{https://github.com/OmarHaggag}{github.com/OmarHaggag}
}

\date{\today}

\begin{document}

\begin{letter}{
    Hiring Manager\\\\
    AI/ML Engineering Team\\\\
    [Company Name]\\\\
    [Company Address]
}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in a part-time contract position in AI/ML engineering. While my primary background is in EDA infrastructure, I have developed substantial hands-on experience with LLMs, RAG systems, and AI-powered automation that positions me uniquely to bridge infrastructure engineering with practical AI implementation.

Over the past two years, I have architected and deployed local LLM infrastructure serving 200+ users in my organization. This involved installing and configuring Ollama, deploying models including Qwen7b and Llama3, and establishing secure access controls for enterprise use. I have gained practical experience in model selection, resource optimization, and scaling inference workloads across available compute resources.

My RAG (Retrieval-Augmented Generation) development experience includes:
\begin{itemize}
    \item Building document processing pipelines with LangChain and LangGraph
    \item Implementing vector databases using ChromaDB and FAISS for efficient retrieval
    \item Creating embeddings workflows and managing knowledge base updates
    \item Integrating RAG systems with internal documentation and code repositories
    \item Using LangSmith for monitoring and optimizing retrieval quality
\end{itemize}

I have also extensively utilized agentic AI tools including VSCode Copilot, Cline, Continue.dev, and Google AI Studio to accelerate my development work. This practical experience with AI-assisted development gives me insight into both the capabilities and limitations of current AI tooling, which I can leverage to design better AI-powered solutions.

My programming skills in Python, combined with my infrastructure background in Linux system administration and DevOps practices, enable me to deploy AI solutions from experimentation through production. I am experienced with containerization, API development, and securing AI services for enterprise deployment.

I am seeking a contract role where I can apply this self-developed AI expertise to real-world problems, particularly in domains where my infrastructure and automation background adds unique value. I am excited about opportunities to work on RAG applications, LLM deployment, or AI-powered automation systems.

Thank you for considering my application. I would welcome the opportunity to discuss how my practical AI implementation experience could contribute to your team's objectives.

\closing{Sincerely,}

\end{letter}

\end{document}
